Palmer Archipelago (Antarctica) penguins: an alternative to Edgar Anderson's iris data

### 2020-06-28 manuscript/manuscript_text.Rmd
actually deal with conflicts (#6)

penguins_kmeans <- ggplot(data = bills_cluster, aes(x = bill_length_mm, 
                                     bill_depth_mm)) +
  geom_text(aes(label=cluster_no, color = species), 
                  size = 4) +
  scale_color_manual(values = c("darkorange","darkorchid","cyan4")) +
  labs(title = "Penguins k-means clustering") +
  theme(legend.position = "bottom")

@@

combo_cluster
```
#### k-means clustering: all numeric variables

@@

### Hierarchical clustering?

@@

>>>>

penguins_kmeans <- ggplot(data = bills_cluster, aes(x = bill_length_mm, 
                                     bill_depth_mm)) +
  geom_text(aes(label=cluster_no, color = species), 
                  size = 4)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
penguin_bill_scatter <- ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point(aes(color = species), size = 2, alpha = 0.7) +
  theme_minimal() +
  scale_color_manual(values = c("darkorange","darkorchid","cyan4")) +
  labs(title = "Penguins k-means clustering") +
  theme(legend.position = "bottom")

@@

combo_cluster
```

#### k-means clustering: all numeric variables

@@

### Clustering (e.g. k-means?)

### Classification (Alison Hill blog post?)

## Differences by islands? 
>>>>>>> 0181779cd02ccdc2413d2698c7029f18572f3757

@@

A Web of Science search reveals that Fisher's 1936 paper has been cited in 7,258 publications (as of June 2020), most often in journals publishing in fields of Computer Science (57% of 7,258 citing references), Mathematics (49%), and Engineering (29%) - most of which we expect are crediting Anderson's *Iris* data, and not Fisher's eugenics work.
